---
title: "Lab Exer2"
output: html_document
date: "2024-03-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

SCRAPING FOR 50

product1 - Microsoft Surface Laptop 5 Super-Thin 13.5 Inch Touchscreen Laptop - Green - Intel EVO 12th Gen Core i7, 16GB RAM, 512GB SSD, Windows 11 Home, UK plug, 2022 Model
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product1 <- data.frame()

for (page in 1:5) {
  link1 <- paste0("https://www.amazon.co.uk/Microsoft-Surface-Laptop-Super-Thin-Touchscreen/product-reviews/B0B9NZJJ1J/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session1 <- bow(link1, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session1) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Microsoft Surface Laptop 5 Super-Thin 13.5 Inch Touchscreen Laptop - Green - Intel EVO 12th Gen Core i7, 16GB RAM, 512GB SSD, Windows 11 Home, UK plug, 2022 Model"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product1 <- rbind(product1, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product1)

```

product2 - ASUS ZenBook Duo UX482EAR 14.0" Dualscreen Full HD Laptop with Touchscreen (Intel i7-1195G7, 16GB RAM, 1TB PCIe SSD, Windows 11, ScreenPad Plus with Stylus Pen) Intel EVO Certified
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product2 <- data.frame()

for (page in 1:5) {
  link2 <- paste0("https://www.amazon.co.uk/ASUS-Touchscreen-ScreenPad-i7-1195G7-Certified/product-reviews/B0BN925W4R/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session2 <- bow(link2, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session2) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "ASUS ZenBook Duo UX482EAR 14.0 Dualscreen Full HD Laptop with Touchscreen (Intel i7-1195G7, 16GB RAM, 1TB PCIe SSD, Windows 11, ScreenPad Plus with Stylus Pen) Intel EVO Certified"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product2 <- rbind(product2, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product2)

```

product3 - ASUS Laptop Vivobook 15 E1504GA 15.6" Full HD Laptop (Intel i3 8-Core Processor, 8GB RAM, 512GB PCIe SSD, Windows 11)
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product3 <- data.frame()

for (page in 1:5) {
  link3 <- paste0("https://www.amazon.co.uk/ASUS-Vivobook-E1504GA-Processor-Windows/product-reviews/B0BZZ8C6WP/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session3 <- bow(link3, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session3) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "ASUS Laptop Vivobook 15 E1504GA 15.6 Full HD Laptop (Intel i3 8-Core Processor, 8GB RAM, 512GB PCIe SSD, Windows 11)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product3 <- rbind(product3, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product3)

```

product4 - ASUS Vivobook M1605YA 16.0" WUXGA Laptop (AMD Ryzen 7-7730U, 16GB RAM, 1TB PCIe SSD, Backlit Keyboard, Windows 11)
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product4 <- data.frame()

for (page in 1:5) {
  link4 <- paste0("https://www.amazon.co.uk/ASUS-Vivobook-M1605YA-7-7730U-Keyboard/product-reviews/B0CLLSFXR3/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session4 <- bow(link4, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session4) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "ASUS Vivobook M1605YA 16.0 WUXGA Laptop (AMD Ryzen 7-7730U, 16GB RAM, 1TB PCIe SSD, Backlit Keyboard, Windows 11)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product4 <- rbind(product4, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product4)
```

product5 - Dell Inspiron 16 5630 16" FHD+ 16:10 Laptop, Intel Core i5-1340P, 16 RAM,512, Intel Iris Xe Graphics,Fingerprint Reader, Backlit Keyboard, Windows 11 Home (Silver)

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product5 <- data.frame()

for (page in 1:5) {
  link5 <- paste0("https://www.amazon.co.uk/Dell-Inspiron-5630-FHD-Fingerprint/product-reviews/B0C7LFTJ3J/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session5 <- bow(link5, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session5) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Dell Inspiron 16 5630 16 FHD+ 16:10 Laptop, Intel Core i5-1340P, 16 RAM,512, Intel Iris Xe Graphics,Fingerprint Reader, Backlit Keyboard, Windows 11 Home (Silver)
"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product5 <- rbind(product5, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  Sys.sleep(3)
}

#View(product5)

```


product6 - Dell Inspiron 14 7430 2-in-1 Laptop, 13th Generation Intel Core i7-1355U, 14" 16:10 FHD+ Touchscreen, 16GB RAM, 512GB SSD, Backlit Keyboard, Fingerprint Reader, Win 11H (Platinum Silver)
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product6 <- data.frame()

for (page in 3:7) {
  link6 <- paste0("https://www.amazon.co.uk/Dell-Inspiron-Laptop-Generation-i7-1355U/product-reviews/B0C7LGC5WH/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session6 <- bow(link6, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session6) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }
  
  productName <- "Dell Inspiron 14 7430 2-in-1 Laptop, 13th Generation Intel Core i7-1355U, 14 16:10 FHD+ Touchscreen, 16GB RAM, 512GB SSD, Backlit Keyboard, Fingerprint Reader, Win 11H (Platinum Silver)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product6 <- rbind(product6, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product6)

```

product7 - Dell G15 5530 15.6-inch FHD 165 Hz Gaming Laptop, Intel Core i7-13650HX, NVIDIA GeForce RTX 4060 8 GB, 16GB RAM, 512GB SSD, Windows 11 Home (Dark Shadow Grey)
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product7 <- data.frame()

for (page in 3:7) {
  link7 <- paste0("https://www.amazon.co.uk/Dell-15-6-inch-i7-13650HX-GeForce-Windows/product-reviews/B0C2J9C3JD/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session7 <- bow(link7, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session7) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Dell G15 5530 15.6-inch FHD 165 Hz Gaming Laptop, Intel Core i7-13650HX, NVIDIA GeForce RTX 4060 8 GB, 16GB RAM, 512GB SSD, Windows 11 Home (Dark Shadow Grey)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product7 <- rbind(product7, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product7)

```


product8 - MSI Katana 17 Inch FHD Gaming Laptop - (Intel Core i7-13620H, Nvidia GeForce RTX 4050, 16GB RAM, 1TB SSD, Windows 11 Home) - Core Black
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product8 <- data.frame()

for (page in 3:7) {
  link8 <- paste0("https://www.amazon.co.uk/MSI-Katana-17-Gaming-Laptop/product-reviews/B0BSXQ9RPS/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session8 <- bow(link8, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session8) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "MSI Katana 17 Inch FHD Gaming Laptop - (Intel Core i7-13620H, Nvidia GeForce RTX 4050, 16GB RAM, 1TB SSD, Windows 11 Home) - Core Black"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product8 <- rbind(product8, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product8)
```

product9 - WAcer Nitro 5 AN515-58 Gaming Laptop - Intel Core i5-12450H, 16GB, 512GB SSD, NVIDIA GeForce RTX 3050 4G, 15.6" FHD IPS 144Hz, Windows 11, Black
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product9 <- data.frame()

for (page in 3:7) {
  link9 <- paste0("https://www.amazon.co.uk/Acer-Nitro-AN515-58-Gaming-Laptop/product-reviews/B0CLSG1QHD/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session9 <- bow(link9, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session9) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Acer Nitro 5 AN515-58 Gaming Laptop - Intel Core i5-12450H, 16GB, 512GB SSD, NVIDIA GeForce RTX 3050 4G, 15.6 FHD IPS 144Hz, Windows 11, Black"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product9 <- rbind(product9, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product9)
```

product10 - Lenovo IdeaPad Slim 3 Chromebook 14 Inch FHD Laptop - (MediaTek Kompanio 520, 4GB RAM, 64GB eMMC, ChromeOS) - Abyss Blue
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product10 <- data.frame()

for (page in 6:10) {
  link10 <- paste0("https://www.amazon.co.uk/Lenovo-IdeaPad-Slim-Chromebook-Laptop/product-reviews/B0C9LZFN32/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session10 <- bow(link10, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session10) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Lenovo IdeaPad Slim 3 Chromebook 14 Inch FHD Laptop - (MediaTek Kompanio 520, 4GB RAM, 64GB eMMC, ChromeOS) - Abyss Blue"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product10 <- rbind(product10, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product10)
```
product11 - Dell Inspiron 14 7430 2-in-1 Laptop, 13th Generation Intel Core i7-1355U, 14" 16:10 FHD+ Touchscreen, 16GB RAM, 512GB SSD, Backlit Keyboard, Fingerprint Reader, Win 11H (Platinum Silver)
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product11 <- data.frame()

for (page in 3:7) {
  link11 <- paste0("https://www.amazon.co.uk/Dell-Inspiron-Laptop-Generation-i7-1355U/product-reviews/B0C7LGC5WH/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session11 <- bow(link11, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session11) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Dell Inspiron 14 7430 2-in-1 Laptop, 13th Generation Intel Core i7-1355U, 14 16:10 FHD+ Touchscreen, 16GB RAM, 512GB SSD, Backlit Keyboard, Fingerprint Reader, Win 11H (Platinum Silver)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product11 <- rbind(product11, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product11)
```

product12 - Lenovo IdeaPad Slim 3 | 15 inch Full HD Laptop | Intel Core i7-13620H | 16GB RAM | 512GB SSD | Windows 11 Home | Abyss Blue
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product12 <- data.frame()

for (page in 3:7) {
  link12 <- paste0("https://www.amazon.co.uk/Lenovo-IdeaPad-Laptop-i7-13620H-Windows/product-reviews/B0CMTS6BLT/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session12 <- bow(link12, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session12) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Lenovo IdeaPad Slim 3 | 15 inch Full HD Laptop | Intel Core i7-13620H | 16GB RAM | 512GB SSD | Windows 11 Home | Abyss Blue"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product12 <- rbind(product12, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product12)
```

product13 - Samsung Galaxy Chromebook Go Wi-Fi Laptop, 11.6 Inch, Celeron Processor, 4GB RAM, 64GB Storage, Silver - Official
```{r}
library(dplyr)f
library(rvest)
library(polite)
library(httr)
library(selectr)

product13 <- data.frame()

for (page in 3:7) {
  link13 <- paste0("https://www.amazon.co.uk/Samsung-Galaxy-Chromebook-Celeron-Storage/product-reviews/B0BTZ5GJ45/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session13 <- bow(link13, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session13) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Samsung Galaxy Chromebook Go Wi-Fi Laptop, 11.6 Inch, Celeron Processor, 4GB RAM, 64GB Storage, Silver - Official"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product13 <- rbind(product13, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product13)
```

product14 - Lenovo IdeaPad 3 | 15 inch Full HD Laptop | Intel Core i5-1135G7 | 8GB RAM | 256GB SSD | Windows 11 Home | Arctic Grey
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product14 <- data.frame()

for (page in 3:7) {
  link14 <- paste0("https://www.amazon.co.uk/Lenovo-Ideapad-15ITL6-Cloudbook-Laptop/product-reviews/B0B5XXJNHB/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session14 <- bow(link14, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session14) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Lenovo IdeaPad 3 | 15 inch Full HD Laptop | Intel Core i5-1135G7 | 8GB RAM | 256GB SSD | Windows 11 Home | Arctic Grey"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product14 <- rbind(product14, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product14)
```

product15 - Lenovo IdeaPad 1 15 inch Full HD Laptop - (AMD Ryzen 5-3500U, 8GB, 256GB SSD, Windows 11 Home in S mode) - Cloud Grey
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product15 <- data.frame()

for (page in 1:5) {
  link15 <- paste0("https://www.amazon.co.uk/Lenovo-IdeaPad-Laptop-Ryzen-Windows/product-reviews/B0BH8DMH1B/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session15 <- bow(link15, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session15) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Lenovo IdeaPad 1 15 inch Full HD Laptop - (AMD Ryzen 5-3500U, 8GB, 256GB SSD, Windows 11 Home in S mode) - Cloud Grey"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product15 <- rbind(product15, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product15)
```

product16 - Apple 2023 MacBook Air Laptop mit M2 Chip: 15.3 Liquid Retina Display, 8GB RAM, 512GB SSD Speicher, beleuchtete Tastatur, 1080p FaceTime HD Camera. Funktioniert mit iPhone/iPad, Mitternachtsblau
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product16 <- data.frame()

for (page in 1:5) {
  link16 <- paste0("https://www.amazon.co.uk/Apple-2023-MacBook-Laptop-Chip/product-reviews/B0C75VLCZY/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session16 <- bow(link16, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session16) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Apple 2023 MacBook Air Laptop mit M2 Chip: 15.3 Liquid Retina Display, 8GB RAM, 512GB SSD Speicher, beleuchtete Tastatur, 1080p FaceTime HD Camera. Funktioniert mit iPhone/iPad, Mitternachtsblau"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product16 <- rbind(product16, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product16)
```

product17 - Apple 2023 MacBook Air Laptop mit M2 Chip: 15.3 Liquid Retina Display, 8GB RAM, 512GB SSD Speicher, beleuchtete Tastatur, 1080p FaceTime HD Camera. Funktioniert mit iPhone/iPad, Space Grau

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product17 <- data.frame()

for (page in 1:5) {
  link17 <- paste0("https://www.amazon.co.uk/Apple-2023-MacBook-Laptop-Chip/product-reviews/B0C75RHVJG/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session17 <- bow(link17, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session17) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Apple 2023 MacBook Air Laptop mit M2 Chip: 15.3 Liquid Retina Display, 8GB RAM, 512GB SSD Speicher, beleuchtete Tastatur, 1080p FaceTime HD Camera. Funktioniert mit iPhone/iPad, Space Grau"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product17 <- rbind(product17, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product17)
```

product18 - Acer Predator Helios 300 Gaming Laptop PC, 15.6 inch Full HD 144Hz 3ms IPS Display, Intel i7-10750H, RTX 2060 6GB, 16GB DDR4, 512GB PCIe NVMe SSD, Wi-Fi 6, American English Backlit Keyboard

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product18 <- data.frame()

for (page in 1:5) {
  link18 <- paste0("https://www.amazon.co.uk/Acer-Predator-i7-10750H-Dual-Channel-PH315-53-72XD/product-reviews/B08842D7JS/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session18 <- bow(link18, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session18) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Acer Predator Helios 300 Gaming Laptop PC, 15.6 inch Full HD 144Hz 3ms IPS Display, Intel i7-10750H, RTX 2060 6GB, 16GB DDR4, 512GB PCIe NVMe SSD, Wi-Fi 6, American English Backlit Keyboard"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product18 <- rbind(product18, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product18)
```

product19 - OPEN BOX Lenovo Legion 5 Gaming Laptop, 15.6" FHD Display, AMD Ryzen 7 5800H, 16GB RAM, 512GB Storage, NVIDIA GeForce RTX 3050Ti, Windows 11 Home, Phantom Blue

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product19 <- data.frame()

for (page in 1:5) {
  link19 <- paste0("https://www.amazon.co.uk/Lenovo-Display-Storage-GeForce-Windows/product-reviews/B09BDGD2TZ/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session19 <- bow(link19, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session19) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "OPEN BOX Lenovo Legion 5 Gaming Laptop, 15.6 FHD Display, AMD Ryzen 7 5800H, 16GB RAM, 512GB Storage, NVIDIA GeForce RTX 3050Ti, Windows 11 Home, Phantom Blue"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product19 <- rbind(product19, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product19)
```

product20 - Samsung Galaxy Book3 360 Wi-Fi Laptop, 15.6 Inch, 13th gen Intel Core i5 Processor, 8GB RAM, 256GB Storage, Graphite - Official

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product20 <- data.frame()

for (page in 1:5) {
  link20 <- paste0("https://www.amazon.co.uk/Samsung-Galaxy-Processor-Storage-Graphite/product-reviews/B0BQRS5RFG/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session20 <- bow(link20, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session20) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Samsung Galaxy Book3 360 Wi-Fi Laptop, 15.6 Inch, 13th gen Intel Core i5 Processor, 8GB RAM, 256GB Storage, Graphite - Official"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product20 <- rbind(product20, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product20)
```
