---
title: "Lab Exer2"
output: html_document
date: "2024-03-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

SCRAPING FOR 50

product1 - Microsoft Surface Laptop 5 Super-Thin 13.5 Inch Touchscreen Laptop - Green - Intel EVO 12th Gen Core i7, 16GB RAM, 512GB SSD, Windows 11 Home, UK plug, 2022 Model
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product1 <- data.frame()

for (page in 1:5) {
  link1 <- paste0("https://www.amazon.co.uk/Microsoft-Surface-Laptop-Super-Thin-Touchscreen/product-reviews/B0B9NZJJ1J/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session1 <- bow(link1, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session1) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Microsoft Surface Laptop 5 Super-Thin 13.5 Inch Touchscreen Laptop - Green - Intel EVO 12th Gen Core i7, 16GB RAM, 512GB SSD, Windows 11 Home, UK plug, 2022 Model"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product1 <- rbind(product1, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product1)

```

product2 - ASUS ZenBook Duo UX482EAR 14.0" Dualscreen Full HD Laptop with Touchscreen (Intel i7-1195G7, 16GB RAM, 1TB PCIe SSD, Windows 11, ScreenPad Plus with Stylus Pen) Intel EVO Certified
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product2 <- data.frame()

for (page in 1:5) {
  link2 <- paste0("https://www.amazon.co.uk/ASUS-Touchscreen-ScreenPad-i7-1195G7-Certified/product-reviews/B0BN925W4R/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session2 <- bow(link2, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session2) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "ASUS ZenBook Duo UX482EAR 14.0 Dualscreen Full HD Laptop with Touchscreen (Intel i7-1195G7, 16GB RAM, 1TB PCIe SSD, Windows 11, ScreenPad Plus with Stylus Pen) Intel EVO Certified"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product2 <- rbind(product2, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product2)

```

product3 - ASUS Laptop Vivobook 15 E1504GA 15.6" Full HD Laptop (Intel i3 8-Core Processor, 8GB RAM, 512GB PCIe SSD, Windows 11)
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product3 <- data.frame()

for (page in 1:5) {
  link3 <- paste0("https://www.amazon.co.uk/ASUS-Vivobook-E1504GA-Processor-Windows/product-reviews/B0BZZ8C6WP/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session3 <- bow(link3, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session3) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "ASUS Laptop Vivobook 15 E1504GA 15.6 Full HD Laptop (Intel i3 8-Core Processor, 8GB RAM, 512GB PCIe SSD, Windows 11)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product3 <- rbind(product3, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product3)

```

product4 - ASUS Vivobook M1605YA 16.0" WUXGA Laptop (AMD Ryzen 7-7730U, 16GB RAM, 1TB PCIe SSD, Backlit Keyboard, Windows 11)
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product4 <- data.frame()

for (page in 1:5) {
  link4 <- paste0("https://www.amazon.co.uk/ASUS-Vivobook-M1605YA-7-7730U-Keyboard/product-reviews/B0CLLSFXR3/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session4 <- bow(link4, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session4) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "ASUS Vivobook M1605YA 16.0 WUXGA Laptop (AMD Ryzen 7-7730U, 16GB RAM, 1TB PCIe SSD, Backlit Keyboard, Windows 11)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product4 <- rbind(product4, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product4)
```

product5 - Dell Inspiron 16 5630 16" FHD+ 16:10 Laptop, Intel Core i5-1340P, 16 RAM,512, Intel Iris Xe Graphics,Fingerprint Reader, Backlit Keyboard, Windows 11 Home (Silver)

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product5 <- data.frame()

for (page in 1:5) {
  link5 <- paste0("https://www.amazon.co.uk/Dell-Inspiron-5630-FHD-Fingerprint/product-reviews/B0C7LFTJ3J/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session5 <- bow(link5, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session5) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Dell Inspiron 16 5630 16 FHD+ 16:10 Laptop, Intel Core i5-1340P, 16 RAM,512, Intel Iris Xe Graphics,Fingerprint Reader, Backlit Keyboard, Windows 11 Home (Silver)
"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product5 <- rbind(product5, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  Sys.sleep(3)
}

#View(product5)

```


product6 - Dell Inspiron 14 7430 2-in-1 Laptop, 13th Generation Intel Core i7-1355U, 14" 16:10 FHD+ Touchscreen, 16GB RAM, 512GB SSD, Backlit Keyboard, Fingerprint Reader, Win 11H (Platinum Silver)
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product6 <- data.frame()

for (page in 3:7) {
  link6 <- paste0("https://www.amazon.co.uk/Dell-Inspiron-Laptop-Generation-i7-1355U/product-reviews/B0C7LGC5WH/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session6 <- bow(link6, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session6) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }
  
  productName <- "Dell Inspiron 14 7430 2-in-1 Laptop, 13th Generation Intel Core i7-1355U, 14 16:10 FHD+ Touchscreen, 16GB RAM, 512GB SSD, Backlit Keyboard, Fingerprint Reader, Win 11H (Platinum Silver)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product6 <- rbind(product6, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product6)

```

product7 - Dell G15 5530 15.6-inch FHD 165 Hz Gaming Laptop, Intel Core i7-13650HX, NVIDIA GeForce RTX 4060 8 GB, 16GB RAM, 512GB SSD, Windows 11 Home (Dark Shadow Grey)
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product7 <- data.frame()

for (page in 3:7) {
  link7 <- paste0("https://www.amazon.co.uk/Dell-15-6-inch-i7-13650HX-GeForce-Windows/product-reviews/B0C2J9C3JD/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session7 <- bow(link7, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session7) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Dell G15 5530 15.6-inch FHD 165 Hz Gaming Laptop, Intel Core i7-13650HX, NVIDIA GeForce RTX 4060 8 GB, 16GB RAM, 512GB SSD, Windows 11 Home (Dark Shadow Grey)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product7 <- rbind(product7, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product7)

```


product8 - MSI Katana 17 Inch FHD Gaming Laptop - (Intel Core i7-13620H, Nvidia GeForce RTX 4050, 16GB RAM, 1TB SSD, Windows 11 Home) - Core Black
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product8 <- data.frame()

for (page in 3:7) {
  link8 <- paste0("https://www.amazon.co.uk/MSI-Katana-17-Gaming-Laptop/product-reviews/B0BSXQ9RPS/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session8 <- bow(link8, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session8) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "MSI Katana 17 Inch FHD Gaming Laptop - (Intel Core i7-13620H, Nvidia GeForce RTX 4050, 16GB RAM, 1TB SSD, Windows 11 Home) - Core Black"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product8 <- rbind(product8, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product8)
```

product9 - WAcer Nitro 5 AN515-58 Gaming Laptop - Intel Core i5-12450H, 16GB, 512GB SSD, NVIDIA GeForce RTX 3050 4G, 15.6" FHD IPS 144Hz, Windows 11, Black
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product9 <- data.frame()

for (page in 3:7) {
  link9 <- paste0("https://www.amazon.co.uk/Acer-Nitro-AN515-58-Gaming-Laptop/product-reviews/B0CLSG1QHD/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session9 <- bow(link9, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session9) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Acer Nitro 5 AN515-58 Gaming Laptop - Intel Core i5-12450H, 16GB, 512GB SSD, NVIDIA GeForce RTX 3050 4G, 15.6 FHD IPS 144Hz, Windows 11, Black"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product9 <- rbind(product9, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product9)
```

product10 - Lenovo IdeaPad Slim 3 Chromebook 14 Inch FHD Laptop - (MediaTek Kompanio 520, 4GB RAM, 64GB eMMC, ChromeOS) - Abyss Blue
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product10 <- data.frame()

for (page in 6:10) {
  link10 <- paste0("https://www.amazon.co.uk/Lenovo-IdeaPad-Slim-Chromebook-Laptop/product-reviews/B0C9LZFN32/ref=cm_cr_dp_d_show_all_btm", page, "?ie=UTF8&reviewerType=all_reviews", page)
  session10 <- bow(link10, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session10) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Lenovo IdeaPad Slim 3 Chromebook 14 Inch FHD Laptop - (MediaTek Kompanio 520, 4GB RAM, 64GB eMMC, ChromeOS) - Abyss Blue"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product10 <- rbind(product10, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  #Sys.sleep(3)
}

#View(product10)
```

